Predictive modeling with cross validation

### 2017-08-24 model fitting/cross_validation.Rmd
fit final model (?)

model <- MASS::stepAIC(fit, direction = "both", k = 2)

@@

@@

# title_beginwh*title_questionmark, log10(text_length), sqrt(newline_ratio), spline = avg_tag_length + device_length
model_spline5 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC") + title_beginwh + title_questionmark*title_beginwh, data = train1)
AIC(model_spline5, k = 2) # 64858.68
```

@@

@@

```{r}
# turn avg_list into a data frame with rownames???
list <- list(allsplines, splinedev, splinetext, splinetag, splinenew, nospline, devtext, sqrtdev, sqrttext, lots)
avg_list <- purrr::map(list, ~get_avgmetrics(.))
avg_list
```

@@

```{r}
newline_text <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + pspline(newline_ratio, df = 0, method = 'AIC')"

sqrtdev <- purrr::map2(trains, tests, ~crossval(newline_text, .x, .y))
sqrtdev
```

>>>>

fit2 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + log10(text_length) + title_questionmark + title_beginwh + sqrt(newline_ratio) + sqrt(avg_tag_score) + text_contain_punct + text_all_lower + update + greeting + as.factor(n_tags) + gratitude + prior_effort + ampm + n_images + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)

model <- MASS::stepAIC(fit2, direction = "both", k = 2)

@@

```{r}
results2 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + 
    contain_unanswered + title_questionmark + sqrt(avg_tag_score) + 
    text_all_lower + update + prior_effort + ampm + weekday + 
    pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, 
    df = 0, method = "AIC"), data = train1)
AIC(results2, k = 2) # 64866.93

@@

# title_beginwh*title_questionmark, log10(text_length), sqrt(newline_ratio), spline = avg_tag_length + device_length
model_spline5 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC") + title_beginwh + title_questionmark*title_beginwh, data = train1)
AIC(model_spline5, k = 2) # 64858.68

# title_beginwh*title_questionmark, log10(text_length), sqrt(newline_ratio), spline = avg_tag_length + device_length + newline_ratio
model_spline5 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC") + title_beginwh + pspline(newline_ratio, df = 0, method = "AIC") + title_questionmark*title_beginwh, data = train1)
AIC(model_spline5, k = 2) # 64841.25
```

@@

##### log10(text_length) + sqrt(newline_ratio) + splines: device_length, avg_tag_length, newline_ratio + interaction between titlebeginwh*title_questionmark

```{r}
vars2 <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, df = 0, method = 'AIC') + title_beginwh + pspline(newline_ratio, df = 0, method = 'AIC') + title_questionmark*title_beginwh"

lots2 <- purrr::map2(trains, tests, ~crossval(vars2, .x, .y))
lots2
```

##### splines on device_length and avg_tag_length (FINAL MODEL???)

```{r}
varsdevtag <- "new_category + as.factor(new_user) + 
    contain_unanswered + title_questionmark + sqrt(avg_tag_score) + 
    text_all_lower + update + prior_effort + ampm + weekday + 
    pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, 
    df = 0, method = 'AIC')"
devtag <- purrr::map2(trains, tests, ~crossval(varsdevtag, .x, .y))
```

@@

```{r}
# turn avg_list into a data frame with rownames???
list <- list(allsplines, splinedev, splinetext, splinetag, splinenew, nospline, devtext, sqrtdev, sqrttext, lots, lots2, devtag)
avg_list <- purrr::map(list, ~get_avgmetrics(.))
avg_list
```

@@

### FINAL MODEL (?)
```{r}
final <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + 
    contain_unanswered + title_questionmark + sqrt(avg_tag_score) + 
    text_all_lower + update + prior_effort + ampm + weekday + 
    pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, 
    df = 0, method = 'AIC'), data = x)
summary(final)
AIC(final, k = 2) # 82957.53

x$predictions <- predict(final, type = "risk")
performance <- cph(Surv(time_until_answer, answered) ~ predictions, data = x)
AIC(performance, k = 2) # 83268.04

final_metrics <- data.frame(HR = exp(performance$coefficients), 
                              LR = round(performance$stats[3],2), 
                              pval = round(performance$stats[5],2), 
                              AIC = stats::AIC(performance, k = 2),
                              Dxy = round(performance$stats[9],2), 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = x)$concordance)
final_metrics
# performance metrics on entire data set are not different from cross validation 
```
